Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-10 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+cfm}
  \caption{%
    \textbf{Combining SICM and confocal fluorescence microscopy.}
    \textbf{a:}
    \textbf{b:} 
    Reprinted with permission from ref \cite{}.
  }
  \label{fig:sicm+cfm}
\end{figure}

Similar to a SICM and wide-field combination, a combination of SICM and confocal FM enables
imaging of the same region and sample with both techniques (Fig.~\ref{fig:sicm+cfm}a). The technical
implementation involves only mounting a SICM onto an inverted confocal FM. The software used to
control the two microscopes does not have to the same as both microscope record data independently 
from one another. However, as the recordings are not simultaneously pixel-by-pixel correlation is hardly,
if at all, possible. Yet, a combination of SICM and z-stacking confocal FM yields more correlating data
than combinations of SICM and wide-field techniques: z-stacking microscopy records data points in 
multiple z planes. After imaging these can be aligned with the SICM data and non-correlating data can be
separated from correlating data. Still, there is a potential mismatch in resolution and the data has to 
be processed after imaging to yield correlation. Yet, this implementation is suitable for all, not only 
flat, fixed samples.

SICM and confocal FM has been combined for the first time by Korchev et al \cite{Korchev2000} in
2000. The group used this combination to verify the volume measurements obtained by SICM. Just a 
year later, further development of this combination enabled simultaneous acqusition of Ca^{2+} 
imaging and topography data \cite{Shevchuk2001}. Afterwards, many different studies using a combination
of SICM and confocal FM have been published:

Topographical information obtained by SICM were successfully correlated with fluorescence signals
of stained cytoskeleton molecules obtained by laser scanning confocal microscopy in platelets 
\cite{Seifert2017}.

In addition, hippocampal neurons, which were very delicate samples with many little protrusions, 
could be investigated with correlated SICM and confocal microscopy. With such a combination active
synaptic boutons could be identified \cite{Novak2013} or the topography could be correlated with 
the distribution (nicht das richtige Wort!?) of the mitochondria \cite{Takahashi2019}.

>>>>

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+cfm}
  \caption{%
    \textbf{Combining SICM and confocal fluorescence microscopy.}
    \textbf{a:} Schematic illustration of the correlating data acquired by combining SICM and confocal FM.
    \textbf{b:} 
    	\textit{Left:} Topography of a neuronal network.
    	\textit{Middle:} Fluorescence of the same neuronal network as depicted on the left.
    	\textit{Right:} Overlay of topography and fluorescence of two regions of interest (ROI 1, ROI 2) from
    	the left and middle image.
    Reprinted with permission from ref \cite{Novak2013}.
  }
  \label{fig:sicm+cfm}
\end{figure}

Similar to a SICM and wide-field combination, a combination of SICM and confocal FM enables
imaging of the same region and sample with both techniques (Fig.~\ref{fig:sicm+cfm}a). The technical
implementation involves mounting a SICM onto an inverted confocal FM. The software used to
control the two microscopes does not have to the same as both microscope record data independently 
from one another. However, as the recordings are not simultaneous, pixel-by-pixel correlation is hardly,
if at all, possible. Yet, a combination of SICM and z-stacking confocal FM yields more correlating data
than combinations of SICM and wide-field techniques as z-stacking microscopy records data points in 
multiple z planes. After imaging, these can be aligned with the SICM data and non-correlating data can be
separated from correlating data. Still, there is a potential mismatch in resolution and the data has to 
be processed after imaging to yield correlation. Yet, this implementation is suitable for all, not only 
flat, fixed samples.

SICM and confocal FM have been combined for the first time by Korchev et al \cite{Korchev2000} in
2000. The group used this combination to verify the volume measurements obtained by SICM. Just a 
year later, further development of this combination enabled simultaneous acqusition of Ca^{2+} 
imaging and topography data \cite{Shevchuk2001}. Afterwards, many different studies using a combination
of SICM and confocal FM were published:

Topographical information obtained by SICM was successfully correlated with fluorescence signals
of stained cytoskeleton molecules obtained by laser scanning confocal microscopy in platelets 
\cite{Seifert2017}.

In addition, hippocampal neurons, which are very delicate samples with many little protrusions, 
could be investigated with correlated SICM and confocal microscopy. With such a combination active
synaptic boutons could be identified \cite{Novak2013} (Fig.~\ref{fig:sicm+cfm}b) and topographical changes
in dendrites were correlated to FM data of mitochondria-containing dendrite regions \cite{Takahashi2019}.
